### 2013-12-08 paper/paper.tex
revision, finished figures

Recently, Gao and Scholl presented a set of studies \cite{gao09,gao10,gao11} demonstrating that certain aspects of motion influence the detection of chasing and the performance in interactive tasks where subjects control chasee with computer mouse. 

@@

For example, in Experiment 2 the subjects controlled a green disc with mouse and tried to avoid contact with a white circle which chased the green circle. 

@@

In their Experiment 4 the chaser was the only circle in the display, so it was easily identified. 

@@

In Experiment 3a the comparison was not between trials, but rather the display was divided into areas which contained darts with different orientation (see figure \ref{fig:exp} A). 

@@

Intuitively however, the center of mass (cross) looks like a much better candidate. 

@@

@@

Still, since the the intended orientation change is perceived as motion, the results can be explained by the influence of motion cues on subjects judgment. 

@@

The design and results were similar to that of Experiment 3a, except that instead of darts the subject tried to avoid white circles whose orientation was determined by two red dots ('eyes', see e.g. figure \ref{fig:vec}).

@@

If we use the shape of the agent to determine the center of mass, this is identical to the point around which the circle was rotated in the Experiment. 

@@

It has been repeatedly demonstrated that if subjects are asked to give the last position of a stimulus that just disappeared from the screen, subject's responses are systematically displaced by factors such as gravity, momentum or shape. 

@@

This is usually done by asking subjects to select this position with mouse or alternatively by selecting which of several probes is nearest to the location where the object disappeared.

@@

Hence we would predict a memory displacement which is influenced by factors that provide cue to the future motion direction. 

@@

To test the second claim we shift the rotation center along the anteroposterior axis of the agent (figure \ref{fig:man}) and measure how this manipulation influences subject's avoidance of wolfpack areas. We need to separate the constant influence of the orientation cues from the manipulated displacement. With bugs we can simply turn off the orientation cues by omitting the eyes and using white circles instead. With darts there is no straightforward way to neutralize the influence of the shape on the perceived displacement. Instead we measure avoidance behavior over a range of displacement values and use linear regression model to separate the two factors in the analysis.\\

@@

Immediately after each trial of the leave-me-alone task one dart/bug disappears while all the remaining objects freezee at their last position. 

@@

Second, we devised a novel distance bisection task (figure \ref{fig:exp}C). 

@@

The task requires continuous real-time adaption to the changing motion pattern of the two agents. 

@@

On the other hand, the connection between the distance bisection and leave-me-alone task may not be obvious. 

@@

However, the are many more agents displayed in the leave-me-alone task and the relevant ones are mostly much closer than the average agent in the bisection task. 
In this respect, the location recall judgments should provide more direct evidence that displacement is also perceived during the leave-me-alone task. \\

@@

Such confound would seriously undermine the conclusions of that study, notably the claim that agent's orientation is important cue to detection of chasing and to the perception of goal-directed motion more generally. %ms hier vielleicht noch ein Paar Referenzen..

@@

\section*{General Methods}
\subsection*{Subjects}
Forty one psychology students ( male) participated in the study in exchange for a course credit. % die mannerzahl kommt noch
All subjects had normal or corrected to normal vision.

\subsection*{Stimulus}
The Stimulus programming followed the description in \cite{gao10} and the examples provided on Brian Scholls web-page. 
The display was divided into four quadrants, each forming a square of 5.9 degrees. 
Three white objects (1.9 degrees in diameter) moved inside each quadrant. 
These objects were either bugs (Experiment 1) or darts (Experiment 2). 
A bug was a circle that had two red eyes drawn on top of it. 
(These were two red circles of size 0.19 degrees, located 0.71 degrees from the center of the white circle and 0.49 degress apart.) 
The dart was a white polygon with four vertices. 
Three of them were located at the perimeter and the remaining vertex was at the origin of the circle. 
The wings of the dart formed an angle of 120 degrees.
The subject steered a a green circle (chasee, 1.2 diameter) with computer mouse. 
The movement was confined to lie within a circular area of 11.75 degrees radius. 
The boundary of the circular area was shown on the screen as a thin gray line. 
The motion of the white objects was generated as follows. 
The objects moved at constant speed of 7.8 degrees per second. 
Each object changed its direction at random intervals with 3 direction changes per second on average. 
The new direction was chosen randomly from a range of -45 to 45 degrees around its current direction. 
The objects were pervasive to each other and upon touching the wall of the designated quadrant they bounced off. \\
The orientation was manipulated as follows. 
Agents were oriented either with their eyes/nose directed towards the agent's location or perpendicular to the agent. 
There were two quadrants with perpendicular orientation and two quandrants with head-on oriented agents (wolfpack). 
The layout of the quadrants was chosen randomly on each trial. \\

@@

Then the agents appeared and the subject tried to avoid contact by moving the green circles within the circular boundary. 

@@

One agent disappeared. 

@@

Whenever possible the computer program tried to select an agent that did not overlap with others and so that perpendicular and wolfpack agents were chosen approximately equally often within each block. \\

@@

The magnitude of this shift was varied across trials. 
Furthermore, we calibrated the manipulation between subjects. 

@@

The trial started after the subject clicked on the green circle. 

@@

\subsection*{Materials and Data}
Subjects gave informed consent to participate in the study and were further given an option to make their data publicly available. 
All subjects agreed. 
The materials and data are available from\\ \url{http://github.com/simkovic/wolfpackRevisited}.

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman13}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting simple model usally a model with separate parameters for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models are most easily formulated and evaluated within bayesian framework.
Finally we report and interpret the estimates of variables of interest - usually the population-level estimates. 
We report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of these modeling decisions in the Results section below. In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
An overview of the models from which we report estimates is given in table \ref{tab:models}. 
Bayesian model requires formulation of prior distributions for the analysis. 
These are not included the table. 
We selected priors such that they do not influence the results of estimation. 
Usually we chose uniform priors, constrained to reasonable range of parameter values (e.g. range $[0,1]$ for mean proportion $\mu_{\mu}$ in S2.2). 
The models were evaluated with STAN 2.0.1 which fits statistical models with Markov chain Monte Carlo sampling. 
In each analysis, four chains were run and the convergence was checked by computing for each parameter an estimate of the potential scale reduction $\hat{R}$ (see \cite{gelman03} p.297). 
In all analyses and for all parameters we ensured that $\hat{R} \leq 1.2$ where $\hat{R} = 1$ upon convergence.
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
The table \ref{tab:ip} links the reported analyses to the output in these files. 
\section*{Results}

@@

The measurements are shown in figure \ref{fig:b5} and summary statistics are given in \ref{tab:b5}. 
The localization judgments (B, C, E, G) are more precise than recall (A, D, F). 
Darts show systematic displacement in the direction of the nose (D-G). 
Bugs show no such displacement although the recall task (A) may be worth further investigation. 
The reported origin is displaced further towards the nose than the center of mass (shown as vertical dashed line at 0.13 in figure \ref{fig:b5}) would suggest. \\
Recall that the task with static stimuli was preceded by task with stimuli where the origin was shifted. 
Does the reported location of static stimuli reflect learning and transfer of knowledge from the previous task? 
The second row (D, E) shows data for subjects who saw the origin shifted towards the nose (dots in figure \ref{fig:man}). 
The data are consistent with a learning account. 
However, in third row (F, G) we would expect a judgment shifted to the left, but we don't observe any reliable difference between the two groups of subjects. 
Finally, there are notable differences among subjects. 
The dark purple subject located the origin at the nose (E) and did so also during recall (D). 
The green subject located the origin behind the dart (E) but only when the stimulus remained on the screen.

@@

\subsubsection*{Darts}
Bisection judgments for dart stimuli (D2.3.1) are shown in panel B of figure \ref{fig:b3}. 
As with bugs we fit a hierarchical model (S3.1) for displacement on each axis. 
The same model can be applied to trials where the origin was shifted (D2.3.2 and D2.3.3). The results for x axis are shown in figure \ref{fig:b3reg} A. 
As expected, the jugments lie on a line with slope approximately equal to 1. 
We can use this fact to include all bisection data in a a single regression model (S3.2). 
The fitted regression line is shown in red in figure \ref{fig:b3reg} A. Its slope is $1.04\; [0.87,1.23]$. 
Of more interest is the line's offset.
It gives the perceived displacement independent of the manipulated displacement (and relative to the nominal zero shown in figure \ref{fig:man}). 
The offset is $0.25\; [0.2,0.29]$ degrees. 
This is considerably larger than zero and larger than the location of center of mass would predict. 
%ms The data are consistent with the judgments of the origin of static darts.
\\
The results of analogous analysis for the displacement due to the orientation of the perpendicular dart are shown in figure \ref{fig:b3reg} B. 
The separate estimates for each condition (S3.1) show that the data points do not lie on a line but rather form a sigmoidal curve. 
If we fit a regression line to the data from different conditions, we observe a slope of $0.88\; [0.63,1.1]$ and a constant offset of $0.15\; [0.09,0.2]$.

\subsubsection*{Circles}
We can fit the regression model (S3.2) to bisection data which used circles with displaced location. 
In this case there is no orientation cue apart from the manipulated displacement. 
The slope on the x axis was $0.86\; [0.01,1.74]$ and $0.5 \;[-0.27,1.3]$ for y axis. These estimates are very imprecise due to small sample size.
%ms dashier in die diskussion schieben
%However, we see that here also the displacement on y axis is smaller than on x axis. This effect is thus most probably a property of the task and does not reflect the true displacement.

\subsection*{Location Recall} 
\subsubsection*{Statistical Modeling} 
In block 1 and 2, we are interested in the direction of the displacement of the recalled location with respect to the actual position of the missing. 
We expect four factors to influence the displacement. 
Their influence is illustrated in figure \ref{fig:vec}. % die beschreibung der abb. anpassen
First, representational gravity pulls objects down along the vertical axis. 
Second, under the influence of representational momentum subjects interpolate future positions along the motion trajectory of object and recall these as its last position. 
Third, we expect that the last position of the green circle (controled by mouse) will influence the judgment. 
In particular we expect that the recalled position will be pulled towards the last mouse position. 
Similar effects of starting position on judgment have been reported in line bisection tasks.% referenz kommt
We call this effect the lazy-hand gravity. 
Finally, we call the displacement in the direction of the circle's orientation (as indicated by the eyes' location or physical displacement in the third block), orientation displacement.\\
Some of the above mentioned factors are correlated due to structure of our task. 
To disentagle their influence, we formulate a regression model. 
We assume that the influence of the four factors is linearly additive. This is illustrated in figure \ref{fig:vectors}. 
Several studies of memory displacement demonstrated additivity. % referenz kommt
Furthermore we assume bivariate gaussian distribution. 
Figure \ref{fig:b1} shows that this assumption is not implausible.
\\ 
More formally, let $\mathbf h =[h_{x}, h_{y}]$ be the vector of the difference between the indicated and the actual position of the missing circle along the two axes. 
Let $\phi_{k}$ be the angle given by the direction of the predictor $k$ (in order as listed in the previous paragraph). 
Then we are interested in the estimates of the regression coefficients $\alpha_k$ given by the equation\\
\begin{equation}
\mathbf h \sim  \mathcal{N}\left(\sum_k \alpha_k \begin{bmatrix} \cos \phi_{k} \\ \sin \phi_{k} \end{bmatrix}, \sigma_h I_{2 \times 2} \right).
\end{equation} 
The regression coefficients are directly interpretable. 
They give the magnitude of the displacement due to each factor in degrees (for $h$ in degrees).
\\
Once more we use hierarchical priors to pool the estimates across subjects and to obtain population estimates. 
A detailed formulation of the model is given in Table \ref{tab:models} (S1.1).

@@

\subsubsection*{Bugs}
We did not replicate the results of Experiment 3b in \cite{gao10}. 
Figure \ref{fig:gao} shows the confidence intervals based on the analyses reported in \cite{gao10} along with the averages for each of our subjects. % das bild kommt noch
All but one subject were located on the upper side of the confidence interval. 
Using the hierarchical beta model we obtained a mean estimate of $0.504 \; [0.481,0.525] $ for the proportion of time spent in wolfpack quadrants. 
Notably the mean estimate of $0.469$ reported by \cite{gao10} is inconsitent with our data.\\

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/exp}
\end{center}
\caption{
{\bf Task Overview}\\
A - Leave-Me-Alone task used by \cite{gao10} in Experiment 3a. 
Display consists of four quadrants. 
Three agents move randomly within each quadrant. 
In two quadrants the agents are oriented towards the green circle (here, the two quadrants on the left) and in other two perpendicular to it. 
Subject's task is to avoid contact with agents. \\
B -Location Recall. 
After 17 seconds the motion stops and one agent vanishes (in this case, the dart located to top-right from the green circle). 
The subject is asked to select the last position where he had seen the agent with a crosshair (not shown).\\ 
C - Distance Bisection task. 
Subject is asked to move the green circle such that it stays equidistant to the two randomly moving agents. 
}
\label{fig:exp}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/man}
\end{center}
\caption{
{\bf Position of Shifted Origin.}
Dots and crosses show where the origin of the dart was set in Block 2 and Block 3 for the dart stimuli. 
Negative values shift the origin towards the nose while positive values shift in the opposite direction.
This choice of negative values follows the following logic. 
If people perceive the origin to be shifted by $k$ degrees in direction of the nose, then we need to shift the position of the nominal origin by $-k$ degrees so that the position of the nominal origin agrees with that of the perceived origin. 
}
\label{fig:man}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/gao}
\end{center}
\caption{
{\bf Failed Replication.}
Dots show the average proportion of time spent in the wolfpack quadrants by subjects in our sample. 
Red line shows the mean estimate reported in \cite{gao10} and the red surface shows the 95\% interval.
}
\label{fig:gao}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/vectors}
\end{center}
\caption{
{\bf Additivity of Different Displacement factors.}
Four different factors influence the displacement (cross), namely representational gravity (black), representational momentum (blue) Lazy Hand Gravity (green) and Agent's Orientation (red). The result of the confluence of these factors is a displacement that is sum of the infividual vectors. One way to visualize vector addition is to translate and superpose the individual vectors over each other so that they form a connected path. This is shown by the opaque arrows.  
}\label{fig:vec}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/b5}
\end{center}
\caption{
{\bf Recall and Localization of Static Stimuli.}
The first row shows the data from Experiment 1 while the remaining rows show data obtained with darts. 
The first column shows recalled position while the remaining columns show positions selected while the stimulus remained visible.
Each cell shows measurements that were rotated around the agents's center such that the direction of eyes/nose is alligned with the positive direction of the horizontal axis.  
Dots show individual trials while the crosses show median for each subject.  
The color of the symbols distinguishes different subjects and is consistent across columns.
The agents are drawn to scale on the background of each cell.  
The dashed line indicates the median displacement in direction of the agent's orientation. 
The shaded area shows the inter-quartile range. 
The dotted line in D-G shows the displacement of darts' center of mass.
}
\label{fig:b5}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/b3}
\end{center}
\caption{
{\bf Results of the Distance Bisection task.}
The results for bugs are shown in A and for darts in B.
Each trial took 17 seconds. We discarded first 2 seconds and computed average mouse displacement with respect to the true mid-point. We 
rotate subjects' judgments around the nominal mid-point such that the wolf is located at 180 degrees and perpendicular agent is at 0 degrees. Each trial is shown above as a dot. Each cross shows an subject average. Furthermore the data from subjects are color-coded.
}
\label{fig:b3}
\end{figure}

@@

@@

\begin{table}[!ht]
\caption{
\bf{Displacement of Static Agents}}
\begin{tabular}{|c|c|c|l|}
\hline
Agent & Task & Figure Cell & Mean Displacement\\
\hline
Bug & Recall & A & $0.06 \; [-0.12,0.25]$ \\
\hline
Bug & Localization & B & $0.01 \; [-0.07,0.01]$ \\
\hline
Circle & Localization & C & $0.02 \; [-0.07,0.11]$ \\
\hline
Dart & Recall & D and F & $0.19 \; [0.12,0.25]$ \\
\hline
Dart & Localization & E and G & $0.22 \; [0.16,0.27]$ \\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\label{tab:b5}
\end{table}

>>>>

Recently, Gao and Scholl demonstrated in a set of studies \cite{gao09,gao10,gao11} that certain aspects of motion influence the detection of chasing and the performance in interactive tasks where subjects control chasee with computer mouse. 

@@

For example, in Experiment 2 \footnote{Demonstration movie from the authors is available at \url{http://tinyurl.com/kcdckbs}} the subjects controlled a green disc with mouse and tried to avoid contact with a white circle which chased the green circle. 

@@

In their Experiment 4 \footnote{Demonstration movie from the authors is available at \url{http://tinyurl.com/lxunkrr}} the chaser was the only circle in the display, so it was easily identified. 

@@

In Experiment 3a \footnote{Demonstration movie from the authors is available at \url{http://tinyurl.com/n53rs7n}} the comparison was not between trials, but rather the display was divided into areas which contained darts with different orientation (see figure \ref{fig:exp} A). 

@@

Intuitively however, the center of mass ($\times$) looks like a much better candidate. 

@@

Furthermore, the travelled distance is larger the further away the perceived origin is from the nominal (compare $\times$ and $+$) 

@@

Still, since the intended orientation change is perceived as motion, the results can be explained by the influence of motion cues on subjects judgment. 

@@

The design and results were similar to that of Experiment 3a, except that instead of darts the subject tried to avoid white circles whose orientation was determined by two red dots ('eyes', see e.g. figure \ref{fig:vec} for an example).

@@

If we use the shape of the agent to determine the center of mass of a bug, this is identical to the point around which the circle was rotated in the Experiment. 

@@

It has been repeatedly demonstrated that if subjects are asked to give the last position of a stimulus that just disappeared on the screen, subject's responses are systematically displaced by factors such as gravity, momentum or shape. 

@@

This is usually done by asking subjects to select the last position with a computer mouse or alternatively by deciding which of several probes is nearest to the location where the object disappeared.

@@

Hence we should predict a memory displacement which is influenced by factors that provide cue to the future motion direction. 

@@

To test the second claim we shift the rotation center along the anteroposterior axis of the agent (figure \ref{fig:man}) and measure how this manipulation influences subject's avoidance of wolfpack areas. We need to separate the constant influence of the orientation cues from the influence of manipulated displacement. With bugs we can simply turn off the orientation cues by omitting the eyes by using white circles as stimuli. With darts there is no straightforward way to neutralize the constant influence of the shape on the perceived displacement. Instead we measure avoidance behavior over a range of displacement values and use linear regression model to separate the two factors in the analysis.\\

@@

Immediately after each trial of the leave-me-alone task one dart/bug disappears while all the remaining objects freezee at their last position (figure \ref{fig:exp} B). 

@@

Second, we devised a novel distance bisection task (figure \ref{fig:exp} C). 

@@

The constantly changing motion pattern of the two agents engages subjects in a dynamic real-time behavior. 

@@

On the other hand, the connection between the distance bisection and leave-me-alone task is so not be obvious. 

@@

However, the are many more agents displayed in the Leave-Me-Alone task and the relevant ones are mostly much closer than the average agent in the bisection task. 
In this respect, the location recall judgments should provide more direct evidence that a displacement is perceived during the leave-me-alone task. \\

@@

%Such confound would seriously undermine the conclusions of that study, notably the claim that agent's orientation is important cue to detection of chasing and to the perception of goal-directed motion more generally. %ms hier vielleicht noch ein Paar Referenzen..

@@

\section*{General Methods}
\subsection*{Subjects}
Forty one psychology students (seven male) participated in the study in exchange for a course credit.
All subjects had normal or corrected to normal vision.

\subsection*{Stimulus}
The Stimulus programming followed the description in \cite{gao10} and the examples provided on Brian Scholls web-page. 
The display was divided into four quadrants, each forming a square of 5.9 degrees. 
Three white objects (1.9 degrees in diameter) moved inside each quadrant. 
These objects were either bugs (Experiment 1) or darts (Experiment 2). 
A bug was a circle that had two red eyes drawn on top of it. 
(These were two red circles of size 0.19 degrees, located 0.71 degrees from the center of the white circle and 0.49 degress apart.) 
The dart was a white polygon with four vertices. 
Three of them were located at the perimeter and the remaining vertex was at the origin of the circle. 
The wings of the dart formed an angle of 120 degrees.
The subject steered a a green circle (chasee, 1.2 diameter) with computer mouse. 
The movement was confined to lie within a circular area of 11.75 degrees radius. 
The boundary of the circular area was shown on the screen as a thin gray line. 
The motion of the white objects was generated as follows. 
The objects moved at constant speed of 7.8 degrees per second. 
Each object changed its direction at random intervals with 3 direction changes per second on average. 
The new direction was chosen randomly from a range of -45 to 45 degrees around its current direction. 
The objects were pervasive to each other and upon touching the wall of the designated quadrant they bounced off. 
As in \cite{gao10} when the green circle overlapped with a white agent the surface of the agent turned red. 
After testing subjects with bugs we got the impression that the red color doesn't motivate subjects enough. 
We therefore added a beep tone which sounded whenever collision happened and as long as the two shapes overlapped (see section \ref{sec:rep} for more details).\\
The orientation was manipulated as follows. 
Agents were oriented either with their eyes/nose directed towards the agent's location or perpendicular to the agent. 
There were two quadrants with perpendicular orientation and two quandrants with head-on oriented agents (wolfpack). 
The layout of the quadrants was chosen randomly on each trial. \\

@@

Then the agents appeared and the Leave-Me-Alone task started (figure \ref{fig:exp} A). The subject tried to avoid contact by moving the green circles within the circular boundary. 

@@

One agent disappeared (figure \ref{fig:exp} B). 

@@

Whenever possible the computer program selected an agent that did not overlap with others and so that perpendicular and wolfpack agents were chosen approximately equally often. \\

@@

We used multiple shift values distributed equiproportionaly and randomly across the block. 
We calibrated the set of shift values as the data became available. 

@@

A trial Distance Bisection task (figure \ref{fig:exp} C) started after the subject clicked on the green circle. 

@@

\subsection*{Materials and Data}
Subjects gave informed consent to participate in the study and were further given an option to make their data publicly available. 
All subjects agreed. 
The materials and data are available from\\ \url{http://github.com/simkovic/wolfpackRevisited}. Demonstration movies of Leave-Me-Alone task and Distance Bisection task are available at \url{http://vimeo.com/81181262} and \url{http://vimeo.com/81181263} respectively.

\subsection*{Statistical Modeling}
In the analyses reported below we follow the approach advocated in \cite{gelman07} and \cite{gelman12}. 
We first design a model that appropriately describes the data. 
We use posterior predictive checking to decide whether the model is acceptable. 
We start by fitting simple model usally a model with separate parameters for each subject. 
We then design a hierarchical model that pools data across subjects \cite{lee11a}. 
Hierarchical models are most easily formulated and evaluated within bayesian framework.
Finally we report and interpret the estimates of variables of interest - usually the population-level estimates. 
We report the mean estimate and the 95 \% interval.\\
The main advantage of this approach is that it gives us flexibility to design complex models that match (or at least approach) the complexity of the processes that generated the data.
The model design involves decisions which may considerably alter the posterior estimates and even the conclusions of the analysis.
We discuss some of these modeling decisions in the Results section below. In general, virtually all results held at least to some degree across all the various models we evaluated and as such the main conclusions of this report are robust.\\
An overview of the models from which we report estimates is given in table \ref{tab:models}. 
Bayesian model requires formulation of prior distributions for the analysis. 
These are not included the table. 
We selected priors such that they do not influence the results of estimation. 
Usually we chose uniform priors, constrained to reasonable range of parameter values (e.g. range $[0,1]$ for mean proportion $\mu_{\mu}$ in S2.2). 
The models were evaluated with STAN 2.0.1 which fits statistical models with Markov chain Monte Carlo sampling. 
In each analysis, four chains were run and the convergence was checked by computing for each parameter an estimate of the potential scale reduction $\hat{R}$ (see \cite{gelman03} p.297). 
In all analyses and for all parameters we ensured that $\hat{R} \leq 1.2$ where $\hat{R} = 1$ upon convergence.
The analyses are documented and can be replicated with the IPython Notebooks available from the project repository.
The table \ref{tab:ip} links the reported analyses to the output in these files. 
\section*{Results}

@@

The measurements are shown in figure \ref{fig:b5} and summary statistics are given in \ref{tab:b5}. 
The localization judgments (B, C, E, G) are more precise than recall (A, D, F). 
Darts show systematic displacement in the direction of the nose (D-G). 
Bugs show no such displacement although the recall task (A) may be worth further investigation. 
The reported origin is displaced further towards the nose than the center of mass (shown as vertical dashed line at $0.13$ in figure \ref{fig:b5}) would suggest. \\
Recall that the task with static stimuli was preceded by task with stimuli where the origin was shifted. 
Does the reported location of static stimuli reflect learning and transfer of knowledge from the previous task? 
The second row (D, E) shows data for subjects who saw the origin shifted towards the nose (dots in figure \ref{fig:man}). 
The data are consistent with a learning account. 
However, in third row (F, G) we would expect a judgment shifted to the left, but we don't observe any reliable difference between the two groups of subjects. 
Finally, there are notable differences among subjects. 
The dark purple subject located the origin at the nose (E) and did so also during recall (D). 
The green subject located the origin behind the dart (E) but only when the stimulus remained on the screen.

@@

\subsubsection*{Darts}
Bisection judgments for dart stimuli (D2.3.1) are shown in panel B of figure \ref{fig:b3}. 
As with bugs we fit a hierarchical model (S3.1) for displacement on each axis. 
The same model can be applied to trials where the origin was shifted (D2.3.2 and D2.3.3). The results for x axis are shown in figure \ref{fig:b3reg} A. 
As expected, the jugments lie on a line with slope approximately equal to 1. 
We can use this fact to include all bisection data in a a single regression model (S3.2). 
The fitted regression line is shown in red in figure \ref{fig:b3reg} A. Its slope is $1.04\; [0.87,1.23]$. 
Of more interest is the line's offset.
It gives the perceived displacement independent of the manipulated displacement (and relative to the nominal zero shown in figure \ref{fig:man}). 
The offset is $0.25\; [0.2,0.29]$ degrees. 
This is considerably larger than zero and larger than the location of center of mass would predict. 
\\
The results of analogous analysis for the displacement due to the orientation of the perpendicular dart are shown in figure \ref{fig:b3reg} B. 
The separate estimates for each condition (S3.1) show that the data points do not lie on a line but rather form a sigmoidal curve. 
If we fit a regression line to the data from different conditions, we observe a slope of $0.88\; [0.63,1.1]$ and a constant offset of $0.15\; [0.09,0.2]$.

\subsubsection*{Circles}
We can fit the regression model (S3.2) to bisection data which used circles with displaced location. 
In this case there is no orientation cue apart from the manipulated displacement. 
The slope on the x axis was $0.86\; [0.01,1.74]$ and $0.5 \;[-0.27,1.3]$ for y axis. These estimates are very imprecise due to small sample size.

\subsection*{Location Recall} 
\subsubsection*{Statistical Modeling} 
In block 1 and 2, we are interested in the direction of the displacement of the recalled location with respect to the actual position of the missing. 
We expect four factors to influence the displacement. 
Their influence is illustrated in figure \ref{fig:vec}. 
First, representational gravity pulls objects down along the vertical axis. 
Second, under the influence of representational momentum subjects interpolate future positions along the motion trajectory of object and recall these as its last position. 
Third, we expect that the last position of the green circle (controled by mouse) will influence the judgment. 
In particular we expect that the recalled position will be pulled towards the last mouse position. 
Similar effects of starting position on judgment have been reported in line bisection tasks.% referenz kommt
We call this effect the lazy-hand gravity. 
Finally, we call the displacement in the direction of the circle's orientation (as indicated by the eyes' location or physical displacement in the third block), orientation displacement.\\
Some of the above mentioned factors are correlated due to structure of our task. 
To disentagle their influence, we formulate a regression model. 
We assume that the influence of the four factors is linearly additive. This is illustrated in figure \ref{fig:vec}. 
Several studies of memory displacement demonstrated additivity. % referenz kommt
Furthermore we assume bivariate gaussian distribution. 
Data in figure \ref{fig:b1} show that this assumption is not implausible.
\\ 
More formally, let $\mathbf h =[h_{x}, h_{y}]$ be the vector of the difference between the indicated and the actual position of the missing circle along the two axes. 
Let $\phi_{k}$ be the angle given by the direction of the predictor $k$ (in order as listed in the previous paragraph). 
Then we are interested in the estimates of the regression coefficients $\alpha_k$ given by the equation\\
\begin{equation}
\mathbf h \sim  \mathcal{N}\left(\sum_k \alpha_k \begin{bmatrix} \cos \phi_{k} \\ \sin \phi_{k} \end{bmatrix}, \sigma_h I_{2 \times 2} \right).
\end{equation} 
The regression coefficients are directly interpretable. 
They give the magnitude of the displacement due to each factor in degrees (for $h$ in degrees).
\\
Once more we use hierarchical priors to pool the estimates across subjects and to obtain population estimates. 
A detailed formulation of the model is given in Table \ref{tab:models} (S1.1).

@@

\subsubsection*{Bugs}
We did not observe the avoidance of wolfpack reported in Experiment 3b in \cite{gao10}. 
Figure \ref{fig:gao} shows the 95\% interval based on the analyses reported in \cite{gao10} along with the averages for each of our subjects.
All but one subject were located on the upper side of the confidence interval. 
Using the hierarchical beta model we obtained a mean estimate of $0.504 \; [0.481,0.525] $ for the proportion of time spent in wolfpack quadrants. 
Notably the mean estimate of $0.469$ reported by \cite{gao10} is inconsitent with our data.\\

@@

\section*{Figure Legends}
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/exp}
\end{center}
\caption{
{\bf Task Overview}\\
A - Leave-Me-Alone task used by \cite{gao10} in Experiment 3a. 
By horizontally and vertically bisecting into two halves we obtain four quadrants. 
Three agents move randomly inside of each quadrant. 
In two quadrants the agents are oriented towards the green circle (the two quadrants on the left) and in other two perpendicular to it. 
Subject's task is to avoid contact with agents. \\
B -Location Recall. 
After 17 seconds of Leave-Me-Alone task the motion stops and one agent vanishes (in this case, the dart located to top-right from the green circle). 
The subject is asked to select with a crosshair (not shown) the last position where he had seen the agent.\\ 
C - Distance Bisection task. 
Subject is asked to move the green circle such that it stays equidistant to the two randomly moving agents. 
}
\label{fig:exp}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/rot}
\end{center}
\caption{
{\bf Rotation perceived as Motion}
The red agent is rotated around the nominal origin (green dot). If the perceived origin lies somewhere between the nominal orgin and agent's nose the nominal rotation is perceived as motion. This is demonstrated for two points: the center of mass located $0.13$ degrees away from origin ($+$) and a point at $0.4$ ($\times$). 
}\label{fig:rot}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/vectors}
\end{center}
\caption{
{\bf Additivity of Different Displacement factors.}
Four different factors influence the displacement (cross), namely representational gravity (black), representational momentum (blue) Lazy Hand Gravity (green) and Agent's Orientation (red). The total displacement due to these factors is a sum of the vectors (shown as arrows) of the four factors. One way to visualize vector addition is to translate and superpose the individual vectors over each other so that they form a connected path. This is shown by the opaque arrows.  
}\label{fig:vec}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/man}
\end{center}
\caption{
{\bf Position of Shifted Origin.}
Dots and crosses show where the origin of the dart was set in Block 2 and Block 3 for the dart stimuli. 
Negative values shift the origin towards the nose while positive values shift in the opposite direction.
This choice of negative values follows the following logic. 
If people perceive the origin to be shifted by $k$ degrees in direction of the nose, then we need to shift the position of the nominal origin by $-k$ degrees so that the position of the nominal origin agrees with that of the perceived origin.}
\label{fig:man}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6.83in]{fig/b5}
\end{center}
\caption{
{\bf Recall and Localization of Static Stimuli.}
The first row shows the data obtained with bugs while the remaining rows show data obtained with darts. 
The latter sample was split into further as is explained in text. This split is shown in the second and third row.
The first column shows recalled position while the remaining columns show positions selected while the stimulus remained visible.
Each cell shows measurements that were rotated around the agents's center such that the direction of eyes/nose is alligned with the positive direction of the horizontal axis.  
Dots show individual trials while the crosses show median for each subject.  
The color of the symbols distinguishes different subjects and is consistent across columns.
The agents are drawn to scale on the background of each cell.  
The dashed line indicates the mean displacement (across all trials) in direction of the agent's orientation. 
The shaded area shows the 95\% interval. 
The dotted line in D-G shows the displacement of darts' center of mass.}
\label{fig:b5}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/b3}
\end{center}
\caption{
{\bf Results of the Distance Bisection task.}
The results for bugs are shown in A and for darts in B.
Each trial took 17 seconds. We discarded first 2 seconds and computed average mouse displacement with respect to the true mid-point. We 
rotate subjects' judgments around the nominal mid-point such that the wolf is located at 180 degrees and perpendicular agent is at 0 degrees. Each trial is shown above as a dot. Each cross shows an subject average. Furthermore the data from subjects are color-coded.}
\label{fig:b3}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.27in]{fig/gao}
\end{center}
\caption{
{\bf Failed Replication.}
Dots show the average proportion of time spent in the wolfpack quadrants by subjects in our sample. 
Red line shows the mean estimate reported in \cite{gao10} and the red surface shows the 95\% interval.}
\label{fig:gao}
\end{figure}

@@

\begin{table}[!ht]
\caption{
\bf{Displacement of Static Agents}}
\begin{tabular}{|c|c|c|l|}
\hline
Agent & Task & Figure Cell & Mean Displacement\\
\hline
Bug & Recall & A & $0.06 \; [-0.12,0.25]$ \\
\hline
Bug & Localization & B & $0.01 \; [-0.07,0.01]$ \\
\hline
Circle & Localization & C & $0.02 \; [-0.07,0.11]$ \\
\hline
Dart & Recall & D and F & $0.19 \; [0.12,0.25]$ \\
\hline
Dart & Localization & E and G & $0.22 \; [0.16,0.27]$ \\
\hline
\end{tabular}
\begin{flushleft}
The 95 \% interval was computed with Student's t distribution ($df = n_s n_v - 1$).
\end{flushleft}
\label{tab:b5}
\end{table}
